%!TEX root = ../../main.tex


%----------%
% ANALYSIS %
%----------%
\section{Analysis}

\newcommand{\tenetmargin}{\vspace{5mm}}

\input{sections/05_analysis/01_se_code_applies}
\input{sections/05_analysis/02_principle_1.tex}
\input{sections/05_analysis/03_principle_2.tex}
\input{sections/05_analysis/04_principle_3.tex}
\input{sections/05_analysis/05_principle_7.tex}

\subsection{The Intent of False News Publishers}

\par Once we have distinguished false news from satire and opinion pieces, it is important to discuss the intent of those who publish such stories. Unfortunately, there is no catch-all case for these publishers.

\par Barring AdBlock, it is not possible to browse the internet without being bombarded by (possibly-targeted) ads. As internet usership grew, so did the efficacy of ad space on the internet. Ads are now widespread and the ultimate goal for some websites is monetization through adspace. \cite{bbc_clickbait} So for many publishers of false news, the motivation is financial --- the intent is to receive clicks. Due to the capitalization of the internet, online writers have turned to incitory headlines and content with the goal of receiving clicks. This is one source of fake news.

\par On April 27th, Facebook published an official transparency report on usage of the social media platform for \emph{information operations}. In this case, Facebook defines \emph{information operations} as ``Actions taken by governments or organized non-state
actors to distort domestic or foreign political sentiment''. \cite{fb_info_ops} Information operations includes the dissemination of false news stories (via bots or otherwise) through social media to disinform the public. Here the motivation is political and the intent is to actively manipulate the beliefs of Facebook's users for personal gain. This amounts to lying, and Kantian ethics could not apply lying as a rule. \cite{kant} Therefore, the usage of fake news for information operations is entirely unethical.

\par Some publishers of fake news have a skewed self-perspective, viewing themselves as fiction writers or prophets. \cite{cbs_fake_news}

%
% PRECEDENTS
%
\subsection{Precedents}

\subsubsection{Burnett v. National Enquirer}

\par TODO: case against National Enquirer by Carol Burnett for libel. National Enquirer paid settlement out of court. Established the possibility of celebrities to sue tabloids for defamation but also established that the national enquirer is not a real newspaper and is not subject to restrictions on journalism.
\cite{burnett_v_ne}
