%!TEX root = ../../main.tex

\subsection{Facebook and the Public}

\par Principle 1 of the Code of Ethics details a software engineer's responsibility to the public. \cite{se_code}

%------%
% 1.02 %
%------%
\subsubsection{Tenet 1.02}

\tenetbox{\ul{Moderate} the \ul{interests} of the \ul{software engineer}, the \ul{employer}, the \ul{client} and the \ul{users} with the \ul{public good}. \cite{se_code}}

\par In the false news debate, Facebook's developers are the \ul{software engineers} involved, as they design, develop, maintain, and test the social media platform on which these false news are circulating. As Facebook develops its own product, Mark Zuckerberg and perhaps his upper echelon also act as the \ul{employer}. 

\par Facebook's users, which include both readers and purveyors of false news, comprise the \ul{users} in this situation. As the end customers of the platform, these users are also Facebook's \ul{clients}.

\par While Facebook affects much of the public due to its size and reach, here the most important aspect of \ul{public good} being affected is the wide disinformation of its \ul{users}.

\par To \emph{moderate} something means to preside over and to bring balance to its extremities. \cite{dictionary} The \ul{interests} of these disparate groups are their various wants and needs. For Facebook to moderate interests means for Facebook to preside over and balance these various wants and needs. 

\dsr{Facebook must balance their needs with the needs and well-being of their users.}
% TODO

%------------------%
% THE USER'S NEEDS %
%------------------%
\subsubsection{The Users' Needs}

\par What do users need?

%------------------%
% THE USER'S NEEDS %
%------------------%
\subsubsection{The Users' Well-Being}

\par How can Facebook maintain users' mental well-being? 

%------------------%
% FACEBOOK'S NEEDS %
%------------------%
\subsubsection{Facebook's Needs}

\par What does Facebook have to gain/lose?

%------%
% 1.04 %
%------%
\subsubsection{Tenet 1.04}

\tenetbox{\ul{Disclose} to \ul{appropriate persons or authorities} any \ul{actual or potential danger} to \ul{the user, the public}, or the environment, that they reasonably believe to be \ul{associated with software or related documents}. \cite{se_code}}

\par This tenet requires that Facebook be cognizant of their users and the public.

\par Facebook's \ul{users} are those with accounts on its social network. Due to the size of Facebook's userbase, those in the \ul{public} have significant overlap with its \ul{users}. But as much of the controvery surrounding false news is politically-charged, we will say that the \ul{public} is the voting population of countries concerned with current events.

\par The \ul{danger} in this situation is of intellectual harm: the threat of wide disinformation. The viral spread of false news has already disinformed many of Facebook's users. The more false news is allowed to spread, the more confusion will spread among Facebook's users as well as others following the news. 

\par Facebook must \ul{disclose} this danger of confusion, meaning Facebook must reveal this danger and inform the \ul{appropriate persons or authorities}.

\par Since Facebook's \ul{users} and the \ul{public} are the ones under threat of disinformation, it would be appropriate for Facebook to inform them. Since the treatment of false news has no historical precent, it is difficult to who the \ul{authorities} are in this situation.

\par As established before, Facebook's social network is the medium through which much of this false news is disseminating. This issue is centered around Facebook's software and Facebook must address it.

\dsr{Reveal the danger of false news to its users, as it is related to their software.}

%------------------------------%
% THE DANGER OF DISINFORMATION %
%------------------------------%
\subsubsection{The Danger of Disinformation}

\par Why is false news dangerous for users?

%-------------------------%
% FACEBOOK'S TRANSPARENCY %
%-------------------------%
\subsubsection{Facebook and Transparency}

\par Was Facebook open in keeping users informed?
