%!TEX root = ../main.tex

\section{Relevant SE Code Tenets}

%------%
% 1.02 %
%------%
\subsection{Tenet 1.02}

\emph{Moderate the interests of the software engineer, the employer, the client and the users with the public good. \cite{se_code}}

As software engineers, those involved are expected to balance their interests with that of the public good.

%------%
% 1.04 %
%------%
\subsection{Tenet 1.04}

\emph{Disclose to appropriate persons or authorities any actual or potential danger to the user, the public, or the environment, that they reasonably believe to be associated with software or related documents. \cite{se_code}}

As software engineers, those involved are expected to disclose that the information in these fake news stories could be false or incitory.

%------%
% 2.07 %
%------%
\subsection{Tenet 2.07}

\emph{Identify, document, and report significant issues of social concern, of which they are aware, in software or related documents, to the employer or the client. \cite{se_code}}

As software engineers, those involved are expected to address the fact that their platforms are creating social rifts and widespread misinformation.

%------%
% 3.03 %
%------%
\subsection{Tenet 3.03}

\emph{Identify, define and address ethical, economic, cultural, legal and environmental issues related to work projects. \cite{se_code}}

As software engineers, those involved are expected to understand that their work has implications in their world at large.

%------%
% 4.02 %
%------%
\subsection{Tenet 4.02}

\emph{Only endorse documents either prepared under their supervision or within their areas of competence and with which they are in agreement. \cite{se_code}}

As software engineers, those involved are expected not to endorse fake news stories that were prepared under means unknown.

%------%
% 4.06 % 
%------%
\subsection{Tenet 4.06}

\emph{Refuse to participate, as members or advisors, in a private, governmental or professional body concerned with software related issues, in which they, their employers or their clients have undisclosed potential conflicts of interest. \cite{se_code}}

As software engineers, those involved are expected not to participate in a fake news platform in which they, their employers, or their clients might have a conflict of interest.

%------%
% 6.08 %
%------%
\subsection{Tenet 6.08}

\emph{Take responsibility for detecting, correcting, and reporting errors in software and associated documents on which they work. \cite{se_code}}

As software engineers, those involved are expected to correct the errors in their software that has led to the proliferation of fake news stories.

%------%
% 7.04 %
%------%
\subsection{Tenet 7.04}

\emph{Review the work of others in an objective, candid, and properly-documented way. \cite{se_code}}

As software engineers, those involved are expected to review and mark stories that appear on their networks without bias.

%------%
% 7.08 %
%------%
\subsection{Tenet 7.08}

\emph{In situations outside of their own areas of competence, call upon the opinions of other professionals who have competence in that area. \cite{se_code}}

As software engineers, those involved are expected to take into account the opinions of professional journalists in determining the validity of stories. 