%!TEX root = ../main.tex

\subsection{Domain Specific Rules}

%------%
% 1.02 %
%------%
\subsubsection{Tenet 1.02}

\emph{\underline{Moderate} the \underline{interests} of the \underline{software engineer}, the employer, the client and the \underline{users} with the \underline{public good}. \cite{se_code}}

Mark Zuckerberg and the employees of Facebook are the \underline{software engineers}, the users are registered Facebook users and posters of fake news, and the \underline{public good} is being affected by widespread misinformation.

For Facebook to \emph{moderate} the conflicting \underline{interests} of these disparate groups means for facebook to 

%------%
% 1.04 %
%------%
\subsubsection{Tenet 1.04}

\emph{Disclose to \underline{appropriate persons or authorities} any \underline{actual or potential danger} to \underline{the user, the public}, or the environment, that they reasonably believe to be associated with software or related documents. \cite{se_code}}

In this situation, the \underline{appropriate persons or authorities} are the fact-checkers behind CrossCheck, \underline{actual or potential danger} refers to misinformation, and \underline{the user and public} are Facebook users and readers of news.

%------%
% 2.07 %
%------%
\subsubsection{Tenet 2.07}

\emph{Identify, document, and report significant \underline{issues of social concern}, of which they are aware, in \underline{software} or related documents, to the employer or the client. \cite{se_code}}

In this situation, the \underline{issues of social concern} are the widespread misinformation of the public and \underline{software} refers to the social media network platform.

%------%
% 3.03 %
%------%
\subsubsection{Tenet 3.03}

\emph{Identify, define and address ethical, economic, cultural, legal and environmental issues related to work projects. \cite{se_code}}

%------%
% 7.04 %
%------%
\subsubsection{Tenet 7.04}

\emph{\underline{Review} the \underline{work} of \underline{others} in an \underline{objective}, \underline{candid}, and \underline{properly-documented} way. \cite{se_code}}

The \emph{work} here refers to articles published by the \emph{others} --- online journalists, real or fake. For Facebook to \emph{review} these articles would be to determine the accuracy of said articles. To be \emph{objective} or \emph{candid} in review means to analyze without bias. To be \emph{properly-documented} in review means to be open and transparent in process. \cite{dictionary}

In applying Tenet 7.04 to our domain, it states that Facebook should \emph{determine the accuracy of online publishers' news articles without bias and be transparent in their methods}.

%------%
% 7.08 %
%------%
\subsubsection{Tenet 7.08}

\emph{In situations outside of their own \underline{areas of competence}, call upon the opinions of \underline{other professionals} who have \underline{competence in that area}. \cite{se_code}}

Facebook software engineers' \emph{areas of competence} are related to their work --- software engineering. As this issue revolves around news, it is outside of their area of competence.

Those with \emph{competence in the area} of news would be journalists, who have dedicated their career to collecting and editing news. \cite{dictionary} Journalists, then are the \emph{other professionals} who are competent in this area.

In applying Tenet 7.08 to our domain, it suggests that Facebook should, \emph{in situations related to news, call upon the opnions of journalists who specialize in that area}. 
